A Spatial AR System for Wide-area Axis-aligned Augmentation of Planar Scenes in Industrial Settings

### 2021-07-06 paper/elsarticle/elsarticle-template.tex
paper

\paragraph{Virtual projector} The placement of the virtual projector determines from which pose the image to be projected is to \textit{appear} to have been projected. This placement is produced according to a small handful of steps. First, we (i) intersect the scene plane with the optical axis (i.e., the ray from the projector's center of projection through the center of the image plane); next, we (ii) rotate the projector's placement about that point of intersection, aligning the optical axis with the scene plane's normal vector and giving an initial virtual projector. Separately, we (iii) carry out steps (i) and (ii) for the camera, giving a virtual camera likewise facing directly downwards to the scene plane. Finally, we (iv) rotate the $X$- and $Y$-axes of the initial virtual projector with those of the virtual camera, which gives the virtual projector. The virtual projector is thus rendered fronto-parallel with the scene plane, enabling projection to the scene plane absent of projective distortions.

Owing to the manner in which we place the virtual projector, the virtual projector's axes and thus the augmentation are aligned with the axes of an image of the scene acquired by a camera, enabling intuitive placement of augmentations in the scene in accordance with the placement of the camera. Note further that a consequence of placing the virtual projector by rotating about the point of intersection of the projector's optical axis with the scene plane is that the center of the projector's image plane remains invariant to projective distortion, i.e., a steerable mirror can be aimed with respect to a point projected from the center of the projector's image plane, further facilitating placement.

>>>>

\paragraph{Virtual projector} The placement of the virtual projector determines from which pose the image to be projected is to \textit{appear} to have been projected. This placement is produced according to a small handful of steps. First, we (i) intersect the scene plane with the optical axis (i.e., the ray from the projector's center of projection through the center of the image plane); next, we (ii) rotate the projector's placement about that point of intersection, aligning the optical axis with the scene plane's normal vector and giving an initial virtual projector. Separately, we (iii) carry out steps (i) and (ii) for the downward-facing camera, giving a virtual camera likewise facing directly\footnote{A physical camera placed to face downwards is likely to not face downwards precisely; in contrast, the virtual camera's optical axis is aligned exactly with the scene plane's normal vector.} downwards to the scene plane. Finally, we (iv) rotate the $X$- and $Y$-axes of the initial virtual projector with those of the virtual camera, which gives the virtual projector. The virtual projector is thus rendered fronto-parallel with the scene plane, enabling projection to the scene plane absent of projective distortions.

Owing to the manner in which we place the virtual projector, the virtual projector's axes and thus the augmentation are aligned with the axes of the downward-facing camera; the placement of the camera thereby intuitively determines the principal axes according to which augmentations are placed. Note further that a consequence of placing the virtual projector by rotating about the point of intersection of the projector's optical axis with the scene plane is that the center of the projector's image plane remains invariant to the placement of the virtual projector, i.e., a steerable mirror can be aimed with respect to a point projected from the center of the projector's image plane, further facilitating placement.
